Fast and optimal centroiding of faint stars

### 2015-07-20 ms/figure.tex
Update figure.tex

Based on inequality (\ref{inequality}), \citet{cramer} defines efficiency of unbiased 
estimators as the ratio of the CRLB and the root-mean-squared-error such that the maximum efficiency 
achievable by an estimator is unity. The closer the root mean-squared 
to the CRLB, the more information about the parameter of interest is preserved, and thus the more efficient 
the estimator is.

@@

Maximum efficiency can be achived by maximum likelihood estimates under the condition. That is, 
the root-mean-squared error, computed for a large ensemble of maximum liklihood estimators can become 
arbitrarily close to the CRLB.

However, the relation (\ref{inequality}) does not necessarily hold for biased estimators. That is, 
the root-mean-squared-error can be smaller than the CRLB (see \citet{lecam}; \citet{hodge}).

Furthermore, an unbiased estimator is called efficient when the root-mean-squared-error 
and the CRLB are equal. Maximum likelihood estimators are asymptotically efficient and maximum 
efficiency can be achieved.

>>>>

Based on inequality (\ref{inequality}), \citet{cramer} defines efficiency of unbiased 
estimators as the ratio of the CRLB and the root-mean-squared-error such that the maximum efficiency 
achievable by an estimator is unity. The closer the root-mean-squared 
to the CRLB, the more information about the parameter of interest is preserved, and thus the more efficient 
the estimator is.

@@

Asymptotically, maximum likelihood estimators can achieve maximum efficiency. That is, for sufficiently large 
number of estimates in a set of maximum likelihood estimates $\{\theta_{\text{ML}}\}$, the root-mean-squared 
error becomes arbitrarily close to the CRLB (see \citet{cramer}; \citet{lecam} for proof).

However, the relation (\ref{inequality}) does not necessarily hold for biased estimators. That is, 
the root-mean-squared-error can be smaller than the CRLB (see \citet{lecam} for examples).
Therefore, we want to investigate the conditions under which, RMSE arising from a given centroiding method 
becomes close to the CRLB, or whether it can become equal to the CRLB in which case the method is \emph{saturating} 
the bound, or whether it can drop below the CRLB in which case the method is \emph{beating} the bound.
